A spiral galaxy's mass distribution uncovered through lensing and dynamics

### 2015-11-18 docs/results_JAMwithNFW_v3.01.tex
Edited modelling section. Some figure corrections.

\paragraph{Including a dark matter halo.} The dynamical modelling attempts in the previous sections suggest that J1331's inner regions have a slightly more roundish and at large radii more massive mass distribution than expected from the distribution of stars alone. A dark matter halo in addition to the stellar component could explain these findings. We therefore proceed by modelling the mass distribution with a) a stellar component, which we get from the light MGE in Table \ref{tab:MGEF814W} (deprojected to the intrinsic $\nu(R,z)$) times a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$), and b) a spherical NFW dark matter component (see Section \ref{sec:model_JAM}) with free parameters halo scale length $r_s$ and circular velocity at the virial radius $v_{200}$. In the JAM modelling we use a 10-Gaussian MGE fit to the classical NFW profile in Equation \ref{eq:NFWprofile}.

@@

\citet{Dutton10} give a relation for halo vs. stellar mass for late-type galaxies. Using the stellar mass estimate for J1331 from \citet{SWELLSI} $m_* = (1.06 \pm 0.25) \cdot 10^{11} M_\odot$ for the Chabrier IMF estimate, we find ${v_{200}} = (202_{-33}^{+44})_{-13}^{+12}$. The first of the two quoted errors is due to the $2\sigma$ scatter in the relation by \citet{Dutton10}. The second error is the propagated error due to the uncertainty in the stellar mass. We use this as a rough estimate for the halo of J1331 and as Gaussian prior on $v_{200}$, 
\begin{equation*}
p(v_{200}) = \mathscr{N}(200~\text{km s}^{-1},40~\text{km s}^{-1}).
\end{equation*}
\\We also use the concentration vs. halo mass relation by \citet{Maccio08} in Equation \ref{eq:Maccio08} as a prior on the concentration, i.e.
\begin{equation*}
p(\log c_{200} \mid v_{200}) = \mathscr{N}\left(\langle \log c_{200} \rangle (M_{200}) \mid 0.105 \right).
\end{equation*}
\\For the velocity anisotropy parameter $\beta$ we will again employ a uniform prior 
\begin{equation*}
p(\beta) = \mathscr{U}(-0.5,+0.5)
\end{equation*}
to exclude very unrealistic anisotropies. The full prior used is then
\begin{eqnarray*}
&&p(\Upsilon_\text{I,*},r_s,v_{200},\beta) \\
&&= \frac{1}{\ln\left( 10 r_s\right)} p(\log c_{200} \mid v_{200}) \cdot p(v_{200}) \cdot p(\beta), 
\end{eqnarray*}
where the factor $1/\ln\left( 10 r_s\right)$ is the Jacobian of the transformation from the halo parameters $(v_{200},\log c_{200})$ to $(v_{200},r_s)$.
\\We restrict the $v_\text{rms}$ fit to a region $R' \lesssim 3.5''$, approximately within the effective half-light radius $R_\text{eff} = 2.6''$. We also include the Einstein mass $M(<R_\text{ein})$ with a 10\% error as an additional constraint in the fit.

\paragraph{Result.} Figure \ref{fig:modelB4_triangle} shows the posterior probability distribution of the fit sampled with an MCMC. Overplotted are also the priors used to constrain the NFW halo. The mean parameters are summarized in Table \ref{tab:modelB4_bestfit}. We find that the best fit NFW halo strives to be more massive and with a higher concentration (due to a smaller $r_s$) than  proposed by the prior. At the same time the model prefers again very negative velocity anisotropies: The sample with the highest probability is pegged at the lower limit of the unifrom prior. Both, the concentrated halo and the low anisotropy are needed to reproduce the central dip of the $v_\text{rms}$ curve. There are slight covariances between $\Upsilon_\text{I,*}$,  $r_s$ and $\beta_z$: The smaller the dark matter contribution in the center (i.e. the larger $\Upsilon_\text{I,*}$), the less concentrated is the halo (i.e. the larger $r_s$), the more velocity anisotropy is needed to reproduce the central dip. As the effect of $v_{200}$ is mostly at larger radii, this parameter doesn't show any covariances - but is also mostly constrained by the prior. \Wilma{[TO DO: Mention the following later in the text: "The $v_\text{rms}$ curve corresponding to the mean best fit values from Table \ref{tab:modelB4_bestfit} is shown in the first panel of Figure \ref{fig:modelB4_vrot}."]} Figure \ref{fig:modelB4_models} illustrates the range of parameters fitting the data according to the full posterior probability function. The model fits the $v_\text{rms}$ data in the inner regions quite well (Figure \ref{fig:modelB4_vrms}) and is also consistent with the Einstein mass (see Figure \ref{fig:modelB4_enclMass}). The extrapolation of the model to larger radii however overestimates the data, does not exhibit a drop around $\sim 6''$ at all and seems to be therefore overall too massive.\\

@@

\begin{figure*}
\centering
\includegraphics[width=0.9\linewidth]{fig/B4_contour_plot_short.ps}
\caption{Posterior probability distribution sampled with MCMC (red dots and histograms) for a JAM model with NFW halo, parametrized by $r_s$ and $v_\text{200}$, a stellar mass distribution generated from the I-band MGE in Table \ref{tab:MGEF814W} and a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$, and constant velocity anisotropy $\beta_z$. Shown are also the priors used for J1331's NFW halo, $\mathscr{N}(200~\text{km s}^{-1},40~\text{km s}^{-1})$ (green) and the concentration vs. halo mass relation by \citet{Maccio08} from Equation \ref{eq:Maccio08} in terms of $v_{200}$ vs. $r_s$ with $1\sigma$ scatter (blue). The MCMC samples are color coded according to their probability (darker red for higher probability); the sample point with the highest probability is marked by a black diamond. The black cross is the mean of the distribution and the ellipses are derived from the covariance of matrix of the sample set and correspond approximately to $1\sigma$ (black solid ellipse) and $2\sigma$ (black dotted ellipse). The histograms of the marginalized 1D distributions are overplotted by the mean (black solid lines) and $1\sigma$ error (black dashed lines), whose values are also quoted in the figure and in Table \ref{tab:modelB4_bestfit}. The grey diamonds mark a random sub-selection of 12 samples; the corresponding models are shown in Figure \ref{fig:modelB4_models}. \Wilma{[TO DO: Use $\text{km s}^{-1}$ instead of km/s]} \Wilma{[TO DO: More space between titles and upper axes tick labels.]}}
\label{fig:modelB4_triangle}
\end{figure*}

\begin{table*}
\centering
\begin{tabular}{llrcl}
\hline
stellar I-band mass-to-light ratio & $\Upsilon_\text{I,*}$ & 4.2 & $\pm$ & 0.2\\
velocity anisotropy & $\beta_z$ & -0.4 & $\pm$ & 0.1 \\
NFW halo scale length & $r_s$ [kpc] & 40 & $\pm$ & 20\\
NFW halo virial velocity & $v_{200}$ [$\text{km s}^{-1}$] & 240 & $\pm$ & 40\\
NFW halo concentration & $c_{200}$ & 8 & $\pm$ & 2 \\
NFW halo mass & $M_{200}$ [$10^{12} M_\odot$] & 5 & $\pm$ & 2\\
\hline
\end{tabular}
\caption{Summary of the best fit parameters of the JAM model with NFW halo from the MCMC exploration in Figure \ref{fig:modelB4_triangle}. The halo mass and concentration are calculated from the the best fit $r_s$ and $v_{200}$.}
\label{tab:modelB4_bestfit}
\end{table*}

\begin{figure*}
\centering
\begin{subfigure}{\textwidth}
  \centering
  \includegraphics[width=0.8\linewidth]{fig/B4_rms_error_curves.ps}
  \caption{Comparison of the $v_\text{rms}$ data with the best fit JAM models.}
  \label{fig:modelB4_vrms}
\end{subfigure}
\begin{subfigure}{.48\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_vcirc.ps}
  \caption{Circular velocity curve.}
  \label{fig:modelB4_vcirc}
\end{subfigure}%
\hspace{.02\textwidth}
\begin{subfigure}{.48\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_projmass.ps}
  \caption{Enclosed mass profile.}
  \label{fig:modelB4_enclMass}
\end{subfigure}
\caption{Best fit JAM model including a NFW halo and velocity anisotropy with parameters given in Table \ref{tab:modelB4_bestfit}. The 12 lines shown correspond to the 12 models randomly drawn from the posterior probability distribution and marked as grey diamonds in Figure \ref{fig:modelB4_triangle}. Overplotted are the Einstein radius (red dotted line) and the effective half-light radius (black dotted line). The blue dashed line marks the radius within which the data and model were fitted. \emph{Panel a)} shows the comparison of the symmetrized $v_\text{rms}$ data (solid blue points) with the best fit JAM models including a NFW halo (red solid lines). Also shown is the non-symmetrized data at larger radii (open blue dots) and an extrapolation of the best fit models, using the same model parameters but the I-band surface brightness MGE for the outer regions of J1331 derived from the Ellipse model (red dashed lines). \emph{Panel b)} shows the circular velocity curve of the total mass (green), and separately the contribution of the stellar mass (yellow, again generated from the MGE in Table \ref{tab:MGEF814W}) and dark matter (grey). \Wilma{[TO DO: make one separate circular velocity plot, that also contains the mass-follows-light with Einstein M/L vcirc and compares it with Aaron's vcirc curve. Ask Aaron for data.]} \emph{Panel c)} shows the corresponding enclosed mass profile. Overplotted is also the Einstein mass at the Einstein radius with a 10\% error, which was used in the fit as an additional constraint. \Wilma{[TO DO: Replace arcsec with '']} \Wilma{[TO DO: Use $\text{km s}^{-1}$ instead of km/s]} \Wilma{[TO DO: Make two figures from this: vrms (shrinked horizontally) and encl Mass should be first and second panel of one figure, and circular velocity curve should be separate figure. ]}}
\label{fig:modelB4_models}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.7\linewidth]{fig/B4_rms_rot_curves_best_model.ps}
\caption{Generating the rotation curve from the JAM model with NFW halo and constant velocity anisotropy with the mean parameters in Table \ref{tab:modelB4_bestfit} and with the best fit rotation parameter $\kappa' = 0.76$ in Equation \ref{eq:kappa_profile} (red solid lines). The second velocity moment in the first panel and the first velocity moment in the second panel with the additional fit parameter $\kappa'$ were fitted to the symmetrized data (solid blue points). The velocity dispersion is simply $\sigma = \sqrt{v_\text{rms}^2 - v_\text{rot}^2}$. At larger radii we compare the unsymmetrized data (open blue dots), the gas kinematics from \citet{SWELLSV} (green diamonds) and a JAM model using the same model parameters but the light distribution MGE generated from the Ellipse model in Figure \ref{fig:MGEouterRegions} as a prediction for the outer regions of J1331 (red dashed lines). The central regions are very well reproduced and we can also nicely predict the rotation curve at larger radii. Only at larger radii the $v_\text{rms}$ and $v_\text{rot}$ overestimate the measurements, probably due to a too massive NFW halo. \Wilma{[TO DO: Replace arcsec with '']} \Wilma{[TO DO: Use $\text{km s}^{-1}$ instead of km/s]}}
\label{fig:modelB4_vrot}
\end{figure*}

>>>>

\paragraph{Including a dark matter halo.} The dynamical modelling attempts in the previous sections suggest that J1331's inner regions have a slightly more roundish and at large radii more massive mass distribution than expected from the distribution of stars alone. A dark matter halo in addition to the stellar component could explain these findings. We therefore proceed by modelling the mass distribution with a) a stellar component, which we get from the light MGE in Table \ref{tab:MGEF814W} (deprojected to the intrinsic $\nu(R,z)$) times a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$), and b) a spherical NFW dark matter component (see Section \ref{sec:model_JAM}) with free parameters halo scale length $r_s$ and circular velocity at the virial radius $v_{200}$. In the JAM modelling we use a 10-Gaussian MGE fit to the classical NFW profile in Equation \eqref{eq:NFWprofile}.

%=======================
\begin{figure*}
\centering
\includegraphics[width=0.9\linewidth]{fig/B4_contour_plot_short.ps}
\caption{Posterior probability distribution sampled with MCMC (red dots and histograms) for a JAM model with NFW halo, parametrized by $r_s$ and $v_\text{200}$, a stellar mass distribution generated from the I-band MGE in Table \ref{tab:MGEF814W} and a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$, and constant velocity anisotropy $\beta_z$. Shown are also the priors used for J1331's NFW halo, $\mathscr{N}(200~\text{km s}^{-1},40~\text{km s}^{-1})$ (green) and the concentration vs. halo mass relation by \citet{Maccio08} from Equation \eqref{eq:Maccio08} in terms of $v_{200}$ vs. $r_s$ with $1\sigma$ scatter (blue). The MCMC samples are color coded according to their probability (darker red for higher probability); the sample point with the highest probability is marked by a black diamond. The black cross is the mean of the distribution and the ellipses are derived from the covariance of matrix of the sample set and correspond approximately to $1\sigma$ (black solid ellipse) and $2\sigma$ (black dotted ellipse). The histograms of the marginalized 1D distributions are overplotted by the mean (black solid lines) and $1\sigma$ error (black dashed lines), whose values are also quoted in the figure and in Table \ref{tab:modelB4_bestfit}. The grey diamonds mark a random sub-selection of 12 samples; the corresponding models are shown in Figure \ref{fig:modelB4_models}. \Wilma{[TO DO: Use $\text{km s}^{-1}$ instead of km/s]} \Wilma{[TO DO: More space between titles and upper axes tick labels.]}}
\label{fig:modelB4_triangle}
\end{figure*}
%=======================

%==============
\begin{table*}
\centering
\begin{tabular}{llrcl}
\hline
stellar I-band mass-to-light ratio & $\Upsilon_\text{I,*}$ & 4.2 & $\pm$ & 0.2\\
velocity anisotropy & $\beta_z$ & -0.4 & $\pm$ & 0.1 \\
NFW halo scale length & $r_s$ [kpc] & 40 & $\pm$ & 20\\
NFW halo virial velocity & $v_{200}$ [$\text{km s}^{-1}$] & 240 & $\pm$ & 40\\
NFW halo concentration & $c_{200}$ & 8 & $\pm$ & 2 \\
NFW halo mass & $M_{200}$ [$10^{12} M_\odot$] & 5 & $\pm$ & 2\\
\hline
\end{tabular}
\caption{Summary of the best fit parameters of the JAM model with NFW halo from the MCMC exploration in Figure \ref{fig:modelB4_triangle}. The halo mass and concentration are calculated from the the best fit $r_s$ and $v_{200}$.}
\label{tab:modelB4_bestfit}
\end{table*}
%==============

@@

\citet{Dutton10} give a relation for halo vs. stellar mass for late-type galaxies. Using the stellar mass estimate for J1331 from \citet{SWELLSI} $m_* = (1.06 \pm 0.25) \cdot 10^{11} M_\odot$ for the Chabrier IMF estimate, we find ${v_{200}} = (202_{-33}^{+44})_{-13}^{+12}$. The first of the two quoted errors is due to the $2\sigma$ scatter in the relation by \citet{Dutton10}. The second error is the propagated error due to the uncertainty in the stellar mass. We use this as a rough estimate for the halo of J1331 and as Gaussian prior on $v_{200}$, 
\begin{equation*}
p(v_{200}) = \mathscr{N}(200~\text{km s}^{-1},40~\text{km s}^{-1}).
\end{equation*}

We also use the concentration vs. halo mass relation by \citet{Maccio08} in Equation \eqref{eq:Maccio08} as a prior on the concentration, i.e.
\begin{equation*}
p(\log c_{200} \mid v_{200}) = \mathscr{N}\left(\langle \log c_{200} \rangle (M_{200}) \mid 0.105 \right).
\end{equation*}

For the velocity anisotropy parameter $\beta$ we will again employ a uniform prior 
\begin{equation*}
p(\beta) = \mathscr{U}(-0.5,+0.5)
\end{equation*}
to exclude very unrealistic anisotropies. The full prior used is then
\begin{eqnarray*}
&&p(\Upsilon_\text{I,*},r_s,v_{200},\beta) \\
&&= \frac{1}{\ln\left( 10 r_s\right)} p(\log c_{200} \mid v_{200}) \cdot p(v_{200}) \cdot p(\beta), 
\end{eqnarray*}
where the factor $1/\ln\left( 10 r_s\right)$ is the Jacobian of the transformation from the halo parameters $(v_{200},\log c_{200})$ to $(v_{200},r_s)$.

%==============
\begin{figure*}
\centering
\begin{subfigure}{.48\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{fig/B4_rms_error_curves.ps}
  \caption{Comparison of the $v_\text{rms}$ data with the best fit JAM models.}
  \label{fig:modelB4_vrms}
\end{subfigure}%
\hspace{.02\textwidth}
\begin{subfigure}{.48\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_projmass.ps}
  \caption{Enclosed mass profile.}
  \label{fig:modelB4_enclMass}
\end{subfigure}
\hspace{\textwidth}
\begin{subfigure}{.48\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_vcirc.ps}
  \caption{Circular velocity curve.}
  \label{fig:modelB4_vcirc}
\end{subfigure}
\caption{Best fit JAM model including a NFW halo and velocity anisotropy with parameters given in Table \ref{tab:modelB4_bestfit}. The 12 lines shown correspond to the 12 models randomly drawn from the posterior probability distribution and marked as grey diamonds in Figure \ref{fig:modelB4_triangle}. Overplotted are the Einstein radius (red dotted line) and the effective half-light radius (black dotted line). The blue dashed line marks the radius within which the data and model were fitted. \emph{Panel a)} shows the comparison of the symmetrized $v_\text{rms}$ data (solid blue points) with the best fit JAM models including a NFW halo (red solid lines). Also shown is the non-symmetrized data at larger radii (open blue dots) and an extrapolation of the best fit models, using the same model parameters but the I-band surface brightness MGE for the outer regions of J1331 derived from the Ellipse model (red dashed lines). \emph{Panel b)} shows the circular velocity curve of the total mass (green), and separately the contribution of the stellar mass (yellow, again generated from the MGE in Table \ref{tab:MGEF814W}) and dark matter (grey). \Wilma{[TO DO: make one separate circular velocity plot, that also contains the mass-follows-light with Einstein M/L vcirc and compares it with Aaron's vcirc curve. Ask Aaron for data.]} \emph{Panel c)} shows the corresponding enclosed mass profile. Overplotted is also the Einstein mass at the Einstein radius with a 10\% error, which was used in the fit as an additional constraint. \Wilma{[TO DO: Replace arcsec with '']} \Wilma{[TO DO: Use $\text{km s}^{-1}$ instead of km/s]} \Wilma{[TO DO: Make two figures from this: vrms (shrinked horizontally) and encl Mass should be first and second panel of one figure, and circular velocity curve should be separate figure. ]}}
\label{fig:modelB4_models}
\end{figure*}
%==============

%==============
\begin{figure*}
\centering
\includegraphics[width=0.7\linewidth]{fig/B4_rms_rot_curves_best_model.ps}
\caption{Generating the rotation curve from the JAM model with NFW halo and constant velocity anisotropy with the mean parameters in Table \ref{tab:modelB4_bestfit} and with the best fit rotation parameter $\kappa' = 0.76$ in Equation \eqref{eq:kappa_profile} (red solid lines). The second velocity moment in the first panel and the first velocity moment in the second panel with the additional fit parameter $\kappa'$ were fitted to the symmetrized data (solid blue points). The velocity dispersion is simply $\sigma = \sqrt{v_\text{rms}^2 - v_\text{rot}^2}$. At larger radii we compare the unsymmetrized data (open blue dots), the gas kinematics from \citet{SWELLSV} (green diamonds) and a JAM model using the same model parameters but the light distribution MGE generated from the Ellipse model in Figure \ref{fig:MGEouterRegions} as a prediction for the outer regions of J1331 (red dashed lines). The central regions are very well reproduced and we can also nicely predict the rotation curve at larger radii. Only at larger radii the $v_\text{rms}$ and $v_\text{rot}$ overestimate the measurements, probably due to a too massive NFW halo. \Wilma{[TO DO: Replace arcsec with '']} \Wilma{[TO DO: Use $\text{km s}^{-1}$ instead of km/s]}}
\label{fig:modelB4_vrot}
\end{figure*}
%==============

We restrict the $v_\text{rms}$ fit to a region $R' \lesssim 3.5''$, approximately within the effective half-light radius $R_\text{eff} = 2.6''$. We also include the Einstein mass $M(<R_\text{ein})$ with a 10\% error as an additional constraint in the fit.

\paragraph{Result.} Figure \ref{fig:modelB4_triangle} shows the posterior probability distribution of the fit sampled with an MCMC. Overplotted are also the priors used to constrain the NFW halo. The mean parameters are summarized in Table \ref{tab:modelB4_bestfit}. We find that the best fit NFW halo strives to be more massive and with a higher concentration (due to a smaller $r_s$) than  proposed by the prior. At the same time the model prefers again very negative velocity anisotropies: The sample with the highest probability is pegged at the lower limit of the unifrom prior. Both, the concentrated halo and the low anisotropy are needed to reproduce the central dip of the $v_\text{rms}$ curve. There are slight covariances between $\Upsilon_\text{I,*}$,  $r_s$ and $\beta_z$: The smaller the dark matter contribution in the center (i.e., the larger $\Upsilon_\text{I,*}$), the less concentrated is the halo (i.e., the larger $r_s$), the more velocity anisotropy is needed to reproduce the central dip. As the effect of $v_{200}$ is mostly at larger radii, this parameter doesn't show any covariances - but is also mostly constrained by the prior. \Wilma{[TO DO: Mention the following later in the text: "The $v_\text{rms}$ curve corresponding to the mean best fit values from Table \ref{tab:modelB4_bestfit} is shown in the first panel of Figure \ref{fig:modelB4_vrot}."]} Figure \ref{fig:modelB4_models} illustrates the range of parameters fitting the data according to the full posterior probability function. The model fits the $v_\text{rms}$ data in the inner regions quite well (Figure \ref{fig:modelB4_vrms}) and is also consistent with the Einstein mass (see Figure \ref{fig:modelB4_enclMass}). The extrapolation of the model to larger radii however overestimates the data, does not exhibit a drop around $\sim 6''$ at all and seems to be therefore overall too massive.\\

@@

@@

### 2015-11-18 docs/results_JAMwithSB_v3.01.tex
Edited modelling section. Some figure corrections.

\paragraph{JAM with lens mass model.} Our first JAM model uses the mass distribution which we found from lensing constraints in Section \ref{sec:results_lensing} to generate an independent prediction for the $v_\text{rms}$ curve following the procedure in Section \ref{sec:model_JAM}. In addition to the flat rotation curve model with $\alpha = 1$ in Table \ref{tab:bestfitlensmodel}, we also investigate a lens model, which was found as a best fit to the lensing images when assuming a slightly rising rotation curve slope of $\alpha=1.1$. The predictions are compared with the data in Figure \ref{fig:JAM_modelL}. The agreement between the lensing prediction and the observed kinematics within $R' \sim 3''$ is striking, especially around the Einstein radius. The $\alpha = 1$ model fits the wings nicely, while the $\alpha = 1.1$ model recreates almost exactly the observed central dip. The sharp drop in $v_\text{rms}$ around $R' \sim 3''$ cannot be reproduced, however. But outside of the Einstein radius our lensing models are only extrapolations and the true constraint is around the Einstein radius.

@@

\paragraph{JAM with "mass-follows-light" and velocity anisotropy.} Our second JAM model is a mass-follows-light model, which are often used in dynamical JAM modelling (e.g. \citet{GlennEC,Cap06}), where the mass distribution is generated by multiplying the intrinsic light distribution $\nu(R,z)$ (the MGE given in Table \ref{tab:MGEF814W} deprojected according to the inclination) by a constant total mass-to-light ratio  $\Upsilon_\text{I,tot}^\text{dyn}$. This assumes that the dark matter is always a constant fraction of the total matter distribution within the region covered by the kinematics. This simplified model sometimes gives good representations of the inner parts of galaxies, where the stellar component dominates. Testing this model for J1331 is also motivated by our findings from lensing in Section \ref{sec:results_lensing}, where around the Einstein radius total and luminous mass seem to have a similar distribution.
\\In addition to the free fit parameter  $\Upsilon_\text{I,tot}^\text{dyn}$, we also allow for a overall constant but non-zero velocity anisotropy $\beta_z$. The best fit is found by minimizing $\chi^2$ between the $v_\text{rms}$ data and model prediction and is demonstrated in Figure \ref{fig:JAM_modelA2}. For $\beta_z$ we impose the fitting limits $\beta_z \in [-0.5,+0.5]$. While the outer parts of galaxies often show radially biased velocity anisotropy up to $\sim 0.5$ (from dynamical modelling of observed elliptical galaxies (e.g. \citet{Kronawitter2000}) and cosmological simulations (e.g. \citet{2004MNRAS.352..535D,2001ApJ...557..533F}), the centers of galaxies are near-isotropic or have  negative velocity anisotropy \citep{2003ApJ...583...92G}. Only in extreme models (e.g. around in-spiralling supermassive black holes \citep{1997NewA....2..533Q}) velocity anisotropies as low as $\sim -1$ have been found. The best fit in Figure \ref{fig:JAM_modelA2} however strives to very negative velocity anisotropies to be able to get the deep central dip in the  $v_\text{rms}$ curve. But $\beta_z = -0.5$ is not even a remotely agreeable fit and lower anisotropies are not to be expected and realistic. We also tested radial profiles for $\beta_z(R)$ of the form proposed by \citet{BaesVanHese}, which was however equally unable to reproduce the data. We conclude, that this is due to the well-known degeneracy between anisotropy and mass profile \Wilma{[TO DO: REF]} and the mass-follows-light model is \emph{not} a good representation of the mass distribution in J1331's inner regions.

@@

\paragraph{JAM with increasing mass-to-light ratio.} In Section \ref{sec:results_lensing} we found from the lensing, that the light distribution might drop faster with radius than the mass distribution. This would correspond to a radially increasing total mass-to-light ratio. As velocity anisotropy alone cannot explain the observed kinematics in a simple a mass-follows-light model, we now allow for an mass-to-light ratio gradient in the JAM modelling to generate a mass model from the light distribution in Table \ref{tab:MGEF814W}. We do this by assigning each of the five Gaussians in the MGE its own total mass-to-light ratio $\Upsilon_{\text{I,tot,}i}$ and replace the total luminosity in Equation \ref{eq:centralItotalL} $L_i$ with the Gaussians total Mass $M_i = \Upsilon_{\text{I,tot,}i} L_i$. We treat the five $\Upsilon_{\text{I,tot,}i}$ as free parameters and only require that $\Upsilon_{\text{I,tot,}j} \geq \Upsilon_{\text{I,tot,}i}$ when the corresponding $\sigma_j \geq \sigma_i$ to ensure an overall mass-to-light ratio that is increasing with radius.

Figure \ref{fig:enclMass_modelG} shows the (local projected) mass-to-light ratio gradient generated by the best fit to the dynamics data, which rises from $\Upsilon_\text{I,tot} = 2.53$ in the center and approaches a value of $\Upsilon_\text{I,tot}$ outside of the fitted region at $R'\gtrsim 3''$ of $\Upsilon_\text{tot} = 7.60$. The central mass-to-light ratio is in agreement with to the mass-to-light ratio $\Upsilon_\text{I,*}^\text{chab} = 2.5 \pm 0.6$, given in Table \ref{tab:previousresults} based on the results of \citet{SWELLSI} assuming a stellar population with an \citet{Chabrier2003} initial mass-function (IMF, see also Section \ref{sec:MLdiscussion}). When assuming that galaxy bulges are generally older and redder in the center \Wilma{[TO DO: REF]}, i.e. $\Upsilon_\text{I,*}$ is rather dropping with increasing radius than increasing, the strong rise of $\Upsilon_\text{I,tot}(R')$ might be due to a strong contribution of dark matter in J1331.

@@

>>>>

\paragraph{JAM with lens mass model.} Our first JAM model uses the mass distribution which we found from lensing constraints in Section \ref{sec:results_lensing} to generate an independent prediction for the $v_\text{rms}$ curve following the procedure in Section \ref{sec:model_JAM}. In addition to the flat rotation curve model with $\alpha = 1$ in Table \ref{tab:bestfitlensmodel}, we also investigate a lens model, which was found as a best fit to the lensing images when assuming a slightly rising rotation curve slope of $\alpha=1.1$. The predictions are compared with the data in Figure \ref{fig:JAM_modelL}. The agreement between the lensing prediction and the observed kinematics within $R' \sim 3''$ is striking. The $\alpha = 1$ model fits the wings around $R_\text{eff}$, while the $\alpha > 1$ model recreates the observed central dip. This is in concordance with observations in other galaxies, where also $\alpha<1$ at large radii. Our lensing model assumes $\alpha(R')=\text{const}$, although these results suggest, that a model with variable $\alpha(R')$ might fit even better, and maybe also reproduce the sharp drop in $v_\text{rms}$ around $R' \sim 3''$. We note however, that the most reliable constraint is around $R_\text{ein}$. Outside of $R_\text{ein}$ lensing models are only extrapolations.

@@

@@

\paragraph{JAM with "mass-follows-light" and velocity anisotropy.} Our second JAM model is a mass-follows-light model, which are often used in dynamical JAM modelling (e.g., \citet{GlennEC,Cap06}), where the mass distribution is generated by multiplying the intrinsic light distribution $\nu(R,z)$ (the MGE given in Table \ref{tab:MGEF814W} deprojected according to the inclination) by a constant total mass-to-light ratio  $\Upsilon_\text{I,tot}^\text{dyn}$. This assumes that the dark matter is always a constant fraction of the total matter distribution within the region covered by the kinematics. This simplified model sometimes gives good representations of the inner parts of galaxies, where the stellar component dominates. Testing this model for J1331 is also motivated by our findings from lensing in Section \ref{sec:results_lensing}, where around the Einstein radius total and luminous mass seem to have a similar distribution.
\\In addition to the free fit parameter  $\Upsilon_\text{I,tot}^\text{dyn}$, we also allow for a overall constant but non-zero velocity anisotropy $\beta_z$. The best fit is found by minimizing $\chi^2$ between the $v_\text{rms}$ data and model prediction and is demonstrated in Figure \ref{fig:JAM_modelA2}. For $\beta_z$ we impose the fitting limits $\beta_z \in [-0.5,+0.5]$. While the outer parts of galaxies often show radially biased velocity anisotropy up to $\sim 0.5$ (from dynamical modelling of observed elliptical galaxies (e.g., \citet{Kronawitter2000}) and cosmological simulations (e.g., \citet{2004MNRAS.352..535D,2001ApJ...557..533F}), the centers of galaxies are near-isotropic or have  negative velocity anisotropy \citep{2003ApJ...583...92G}. Only in extreme models (e.g., around in-spiralling supermassive black holes \citep{1997NewA....2..533Q}) velocity anisotropies as low as $\sim -1$ have been found. The best fit in Figure \ref{fig:JAM_modelA2} however strives to very negative velocity anisotropies to be able to get the deep central dip in the  $v_\text{rms}$ curve. But $\beta_z = -0.5$ is not even a remotely agreeable fit and lower anisotropies are not to be expected and realistic. We also tested radial profiles for $\beta_z(R)$ of the form proposed by \citet{BaesVanHese}, which was however equally unable to reproduce the data. We conclude, that this is due to the well-known degeneracy between anisotropy and mass profile \Wilma{[TO DO: REF]} and the mass-follows-light model is \emph{not} a good representation of the mass distribution in J1331's inner regions.

\paragraph{JAM with increasing mass-to-light ratio.} In Section \ref{sec:results_lensing} we found from the lensing, that the light distribution might drop faster with radius than the mass distribution. This would correspond to a radially increasing total mass-to-light ratio. As velocity anisotropy alone cannot explain the observed kinematics in a simple a mass-follows-light model, we now allow for an mass-to-light ratio gradient in the JAM modelling to generate a mass model from the light distribution in Table \ref{tab:MGEF814W}. We do this by assigning each of the five Gaussians in the MGE its own total mass-to-light ratio $\Upsilon_{\text{I,tot,}i}$ and replace the total luminosity in Equation \eqref{eq:centralItotalL} $L_i$ with the Gaussians total Mass $M_i = \Upsilon_{\text{I,tot,}i} L_i$. We treat the five $\Upsilon_{\text{I,tot,}i}$ as free parameters and only require that $\Upsilon_{\text{I,tot,}j} \geq \Upsilon_{\text{I,tot,}i}$ when the corresponding $\sigma_j \geq \sigma_i$ to ensure an overall mass-to-light ratio that is increasing with radius.

@@

Figure \ref{fig:enclMass_modelG} shows the (local projected) mass-to-light ratio gradient generated by the best fit to the dynamics data, which rises from $\Upsilon_\text{I,tot} = 2.53$ in the center and approaches a value of $\Upsilon_\text{I,tot}$ outside of the fitted region at $R'\gtrsim 3''$ of $\Upsilon_\text{tot} = 7.60$. The central mass-to-light ratio is in agreement with to the mass-to-light ratio $\Upsilon_\text{I,*}^\text{chab} = 2.5 \pm 0.6$, given in Table \ref{tab:previousresults} based on the results of \citet{SWELLSI} assuming a stellar population with an \citet{Chabrier2003} initial mass-function (IMF, see also Section \ref{sec:MLdiscussion}). When assuming that galaxy bulges are generally older and redder in the center \Wilma{[TO DO: REF]}, i.e., $\Upsilon_\text{I,*}$ is rather dropping with increasing radius than increasing, the strong rise of $\Upsilon_\text{I,tot}(R')$ might be due to a strong contribution of dark matter in J1331.
